Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-29 colt-21/cvx-flats.tex
fixing projection stuff in appendix

\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
  Given target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that $\exists L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
\end{definition}
A priori, this definition does not really make sense given a target statistic.
In Definition~\ref{def:consistent-prop}, we formalize consistency with respect to a property so that we can study $\conscvx(\gamma)$. \jessiet{Do we want to just talk about $\ell$ here?}\raft{I didn't think about the target property vs target loss point.  Let's discuss.}

@@

\begin{lemma}
	  \label{lem:convex-flats-inf-dim}
	Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
	When $\Y = \reals$, we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
        \footnote{This assumption is for technical convenience, though we suspect it is strictly stronger than necessary.\raf{This assumption is for technical convenience...}}
	For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{lemma}
\begin{proof}
  As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
  We proceed in two cases, depending on $|\Y|$. \jessiet{Seems really pedantic, but do we need to specify $\Y$ finite or $\Y = \reals$?  Since, for example, $\Y = \mathbb{Z}$ doesn't fit in either case, but isn't ruled out by our Lemma statement.}

@@

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
%and in particular, $\conscvx(\gamma) \geq d + 1$. 
%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$, where $L\in\Lcvx_d$, and let $\Gamma = \prop{L}$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a $d$-flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.
    If no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\eliccvx(\gamma) \geq d+1$, and recall $\conscvx(\gamma) \geq \eliccvx(\gamma)$ by Corollary~\ref{cor:elic-lb-consis-dim}.
\end{proof}

@@

%commenting out 01.25.2021 since we really just need one direction.
%\begin{lemma}\label{lem:p-boundary-fsd}
%	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
%	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
%	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
%\end{lemma}
%\begin{proof}
%	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
%	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.
%	
%	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
%	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
%	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e. $p \not \in \relint{\simplexp}$), it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
%	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
%	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
%	%commented out 05.26.2020
%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
%	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
%	%	\begin{align*}
%	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
%	%	\end{align*}
%	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
%	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
%	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
%	%	
%	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
%	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
%	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
%	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
%	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
%	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
%	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
%	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
%\end{proof}

\hariresult*
\begin{proof}
  Let $L \in \Lcvx_d$ elicit $\Gamma$ be a calibrated surrogate for $\ell$, and consider $\Y^{\proj(q)} := \supp(q)$ for any $q \in \simplex$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y^{\proj(q)}$.
  \raft{I'm not getting the $\proj(q)$ stuff.  It would help if you defined $\proj(q)$, but even so, I suspect there is a more direct approach.  E.g. you define all these $\proj(q)$ versions and then just take the primed versions to be equal.  I'd suggest starting from scratch and thinking through what exactly you need.}
  Take $L^{\proj(q)} := L|_{\Y^{\proj(q)}}$ and $\ell^{\proj(q)} := \ell|_{\Y^{\proj(q)}}$.
  Observe that for all $q \in \simplex$, we have $\gamma(q) = \gamma^{\proj(q)}(B(q))$.

  In particular, take $\Y' = \Y^{\proj(p)}, L' = L^{\proj(p)}$, and $\ell' = \ell^{\proj(p)}$. 
  By consistency, we have $L$ indirectly eliciting $\gamma$.

	Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $B : q \mapsto \{q_{y} \mid y > 0\}$, and in particular, $p' = B(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
	Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and .

	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq  \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.\footnote{To reason about $\dim(\affhull(\simplexp)) = \|p\|_0 - 1$, observe that the uniform distribution on $\simplexp$ has full support and therefore requires $\|p\|_0 - 1$ elements in its basis.}
	%which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.
	%Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$. \jessie{How to get rid of sub p notation here?}
	%Therefore, $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$
	\raft{Might be nicer on the reader to add one more step for $\|p\|_0$. Also, I just realized we are using $p\in\simplex$ here, but then $p$ can't be in $F\subseteq\Delta_{\Y'}$ ($p$ is an $n$-vector). So maybe we need a $p'$ too.\jessie{Is this better now?  Slash can we remove this comment?}}
	Additionally, $\Scr_F(p') \subseteq \Sc_{\gamma'_r}(p')$ by subset inclusion of the sets themselves.
	Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$ trivially.
	%By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p')$.
	Chaining these results, we obtain 
	\begin{align*}
	\dim(\Sc_{\gamma_r}(p)) &\geq \dim(\Sc_{\gamma'_r}(p'))  \geq \dim(\Scr_F(p')) \geq \|p\|_0 - 1 - d~.~
	\end{align*}
%
%	this yields the bound $\dim(\spn(F-\{p\})) \geq \|p\|_0 - 1 - d$.
%	Chaining inequalities, we then have $\dim(\Sc_{\gamma'_r}(p)) \geq \dim(\spn(F - \{p\})) \geq \|p\|_0 - d- 1$ as Lemma~\ref{lem:feas-sub-is-a-flat} states $F - \{p\}$ is a subspace of $\Sc_{\gamma'_r}(p)$.
%	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
	%
	%
	%\old version of the proof from NeurIPS or before - 01.21.2021
	%	First, for intuition, consider $p \in \relint{\simplex}$. 
	%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
	%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
	%
	%	
	%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
	%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
	%	
	%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
	%	\begin{align*}
	%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
	%	\end{align*}
	%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
	%
	%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
	%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
	%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
	%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}

>>>>

\begin{definition}[Convex Consistency Dimension]\label{def:cvx-consistency-dim}
  Given target loss $\ell:\R \times\Y \to \reals$ or statistic $\gamma: \P \toto \R$, its \emph{convex consistency dimension} $\conscvx(\cdot)$ is the minimum dimension $d$ such that $\exists L \in \Lcvx_d$ and link $\psi$ such that $(L,\psi)$ is consistent with respect to $\ell$ or $\gamma$.
%	\btw{Maybe take out of definition environment, but (a) I'd worry that people wouldn't be able to find the definition when we use it later, and (b) I'm hoping we can make the distinction very clear, which now is achieved by the parallel definitions}
\end{definition}
See Definition~\ref{def:consistent-prop} for consistency with respect to a property.

@@

\begin{lemma}
  \label{lem:convex-flats-inf-dim}
  Let $\Gamma:\P \toto \reals^d$ be (directly) elicited by $L \in \Lcvx_d$ for some $d\in\mathbb{N}$.
  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.%
  \footnote{This assumption is for technical convenience, though we suspect it is strictly stronger than necessary.\raf{This assumption is for technical convenience...}}
  For all $u\in\range\Gamma$ and $p\in\Gamma_u$, there is some $V_{u,p}:\Y\to\reals^d$ such that $p \in \zeros{V_{u,p}} \subseteq \Gamma_u$.
\end{lemma}
\begin{proof}
  As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p}$. 
  We proceed in two cases, depending on $|\Y|$.

@@

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
  Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
  Let $\Y$ be either a finite set, or $\Y = \reals$, in which case we assume each $p\in\P$ admits a Lebesgue density supported on the same set for all $p\in\P$.
  Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
If there is no $d$-flat $F$ with $p \in F \subseteq \gamma_r$, then $\conscvx(\gamma) \geq \eliccvx(\gamma) \geq d + 1$.%, 
%and in particular, $\conscvx(\gamma) \geq d + 1$. 
%no $L\in\Lcvx_d$ indirectly elicits $\gamma$
%there is no surrogate $L \in \Lcvx_d$ that is consistent with respect to $\gamma$.
%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$, where $L\in\Lcvx_d$, and let $\Gamma = \prop{L}$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{lem:convex-flats-inf-dim}, we know there is a $d$-flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.
    If no flat $F$ satisfies the above conditions, then no $L\in\Lcvx_d$ indirectly elicits $\gamma$, so $\eliccvx(\gamma) \geq d+1$, and recall $\conscvx(\gamma) \geq \eliccvx(\gamma)$ by Corollary~\ref{cor:elic-lb-consis-dim}.
\end{proof}

@@

commenting out 01.25.2021 since we really just need one direction.
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$ (i.e. $p \not \in \relint{\simplexp}$), it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
	%commented out 05.26.2020
	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
	%	\begin{align*}
	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
	%	\end{align*}
	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
	%	
	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
\end{proof}

\hariresult*
\begin{proof}
  Let $L \in \Lcvx_d$ be a calibrated surrogate for $\ell$, and let $\Gamma := \prop[\simplex]{L}$.
  Consider $\Y' := \{y\in\Y : p_y > 0\}$ and $p' = (p_y)_{y\in\Y'} \in \Delta_{\Y'}$.
  Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.
  Define $h:\Delta_{\Y'} \to \Delta_\Y$ such that $h(q') = q$ such that $q_y = q'_y$ for $y\in\Y'$ and $q_y = 0$ otherwise.
  Take $\Gamma' = \Gamma \circ h$, $\gamma' = \gamma \circ h$.

  \raf{Show that $L'$ indirectly elicits $\gamma'$.}
  By consistency, we have $L$ indirectly eliciting $\gamma$.
  Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $B : q \mapsto \{q_{y} \mid y > 0\}$, and in particular, $p' = B(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
  Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
  This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and .

  \raf{Show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$}
  Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$...

  As $L'$ indirectly elicits $\gamma'$, by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
  Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\Scr_F(p')) \geq  \dim(\affhull(\simplexp)) - d = \|p\|_0 - 1-d$.\footnote{To reason about $\dim(\affhull(\simplexp)) = \|p\|_0 - 1$, observe that the uniform distribution on $\simplexp$ has full support and therefore requires $\|p\|_0 - 1$ elements in its basis.}
  % which gives $\dim(\Scr_F(p')) \geq \dim(\spn(\P_{p'})) - d$.
  % Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$. \jessie{How to get rid of sub p notation here?}
  % Therefore, $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$
  \raft{Might be nicer on the reader to add one more step for $\|p\|_0$. Also, I just realized we are using $p\in\simplex$ here, but then $p$ can't be in $F\subseteq\Delta_{\Y'}$ ($p$ is an $n$-vector). So maybe we need a $p'$ too.\jessie{Is this better now?  Slash can we remove this comment?}}
  Additionally, $\Scr_F(p') \subseteq \Sc_{\gamma'_r}(p')$ by subset inclusion of the sets themselves.
  % By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p')$.
  Chaining these results, we obtain 
  \begin{align*}
    \dim(\Sc_{\gamma_r}(p)) &\geq \dim(\Sc_{\gamma'_r}(p'))  \geq \dim(\Scr_F(p')) \geq \|p\|_0 - 1 - d~.~
  \end{align*}
  % 
  %	this yields the bound $\dim(\spn(F-\{p\})) \geq \|p\|_0 - 1 - d$.
  %	Chaining inequalities, we then have $\dim(\Sc_{\gamma'_r}(p)) \geq \dim(\spn(F - \{p\})) \geq \|p\|_0 - d- 1$ as Lemma~\ref{lem:feas-sub-is-a-flat} states $F - \{p\}$ is a subspace of $\Sc_{\gamma'_r}(p)$.
  %	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
  % 
  % 
  % \old version of the proof from NeurIPS or before - 01.21.2021
  %	First, for intuition, consider $p \in \relint{\simplex}$. 
  %	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
  %	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
  % 
  %	
  %	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
  %	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
  %	
  %	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
  %	\begin{align*}
  % \forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
  % \end{align*}
  %	Therefore, we have $L'$ calibrated with respect to $\ell'$.
  % 
  %	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
  %	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
  %	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
  %	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
  %	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}
